% !TEX TS-program = xelatex
\documentclass[11pt, a4paper]{awesome-cv}

\geometry{left=1.4cm, top=1.1cm, right=1.4cm, bottom=1.1cm, footskip=.5cm}
\fontdir[fonts/]

\colorlet{awesome}{awesome-red}
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\name{Kevin}{Tongue}
\position{Double Degree – Mechanical Engineering \& Master in Numerical Solid Mechanics}
\address{65, Rue Jean Parot, 42000 Saint-Étienne, France}
\mobile{(+33) 6 98 06 37 69}
\email{tonguekevin00@gmail.com}
\github{tiffank1802}
\linkedin{tongue-kevin-52b100330}

%% v2
\begin{document}
\makecvheader

%-------------------------------------------------------------------------------
%  EDUCATION
%-------------------------------------------------------------------------------
\cvsection{Education}
\begin{cventries}

  \cventry
    {Double Degree – Engineering in Mechanical Engineering \& Master 2 in Numerical Solid Mechanics}
    {Centrale Lyon -- ENISE \& \'Ecole Nationale Sup\'erieure Polytechnique de Yaound\'e (ENSPY)}
    {Saint-Étienne, France / Yaoundé, Cameroon}
    {2020 -- 2026 (expected)}
    {
      \begin{cvitems}
        \item \textbf{Specialisation:} Mechanical design, advanced numerical simulation, and computational mechanics.
        \item \textbf{Key courses (Master):} Finite Element Method, Continuum Mechanics, Fracture Mechanics, Structural Dynamics, Nonlinear Mechanics, Uncertainty Quantification, Design of Experiments, Residual Stress Analysis, Fluid Dynamics, Heat Transfer, Materials Science.
        \item \textbf{Key courses (Engineering):} Solid Mechanics, Thermodynamics, Machine Design, Manufacturing Processes, System Dynamics, Signal Processing, Applied Mathematics.
      \end{cvitems}
    }

\end{cventries}

%-------------------------------------------------------------------------------
%  RESEARCH & PROFESSIONAL EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Research \& Professional Experience}
\begin{cventries}

  \cventry
    {Master Internship – Deterministic–Stochastic Coupling for Granular Segregation (DEM + Markov Chains)}
    {IMT Mines Albi \& IMT Mines Saint-\'Etienne}
    {Albi / Saint-Étienne, France}
    {Mar. 2026 -- Sep. 2026}
    {
      \begin{cvitems}
        \item Coupled Discrete Element Method (DEM) simulations with an inhomogeneous Markov chain model to statistically characterise granular segregation dynamics in mixing devices.
        \item Extracted particle-scale transition probabilities from DEM outputs; developed stochastic models linking microscopic particle dynamics to macroscopic distributions.
        \item Designed and executed a Design of Experiments (DoE) plan and performed Monte Carlo sensitivity analysis for uncertainty quantification (UQ).
        \item Implemented end-to-end numerical pipelines in Python (NumPy, SciPy, PyTorch, Matplotlib) including data fusion, signal processing, and model validation.
      \end{cvitems}
    }

  \cventry
    {Research Project – Nonlinear FEM Solver for Fatigue Failure Prediction (Dang Van Criterion)}
    {Centrale Lyon -- ENISE}
    {Saint-\'Etienne, France}
    {Oct. 2025 -- Mar. 2026}
    {
      \begin{cvitems}
        \item Implemented a 3D nonlinear finite element solver in Python/C++ covering static, modal, and transient dynamic analyses.
        \item Applied and validated the Dang Van multiaxial fatigue criterion, including critical plane determination (Agard et al.\ optimisation methodology).
        \item Validated results against analytical benchmarks and Abaqus reference solutions; produced structured technical documentation.
        \item Deployed as a web application: \texttt{huggingface.co/spaces/ktongue/simulations\_apps}
      \end{cvitems}
    }

  \cventry
    {Research Project – Physics-Informed Neural Networks (PINN) for Material Identification}
    {Centrale Lyon -- ENISE (collaboration with LTDS Laboratory)}
    {Saint-Étienne, France}
    {2025}
    {
      \begin{cvitems}
        \item Built a Physics-Informed Neural Network (PINN) in PyTorch coupling deep learning with physical constraints (elasticity, heat equation, plasticity criteria).
        \item Performed inverse identification of constitutive law parameters from compression test data provided by the LTDS laboratory; validated the identified law via FEM simulations.
        \item Implemented data-driven surrogate modelling pipeline: preprocessing, training loop, hyperparameter tuning, and result visualisation.
        \item Deployed at: \texttt{huggingface.co/spaces/ktongue/material\_identification}
      \end{cvitems}
    }

  \cventry
    {Laboratory Coursework – Surface Integrity and Residual Stress Characterisation in Machining}
    {Centrale Lyon -- ENISE}
    {Saint-\'Etienne, France}
    {2023 -- 2024}
    {
      \begin{cvitems}
        \item Measured residual stresses induced by machining operations using laser-based spectroscopy techniques, and correlated results with cutting parameters and tool wear state.
        \item Conducted experimental micro-hardness mapping (Vickers micro-indentation) on machined 42CrMo4 steel specimens, comparing surface and core hardness across new vs.\ worn cutting inserts and parallel vs.\ perpendicular cutting directions.
        \item Characterised microstructure and tool wear mechanisms using Scanning Electron Microscopy (SEM) and Energy-Dispersive X-ray Spectroscopy (EDXS) to identify coating degradation and material composition changes at cutting edges.
        \item Analysed the influence of machining operations on surface integrity (hardness gradients, microstructural alteration, residual stress state) to define recommendations ensuring part integrity.
      \end{cvitems}
    }

  \cventry
    {Academic Project – Microstructure Partitioning Model (Image Segmentation)}
    {\'Ecole des Mines de Saint-\'Etienne}
    {Saint-Étienne, France}
    {Feb. -- Jun. 2025}
    {
      \begin{cvitems}
        \item Processed and segmented microstructural images using Python (NumPy, OpenCV, SciPy); performed geometric feature extraction and statistical characterisation of material phases.
        \item Developed modular segmentation and classification algorithms applicable to materials with heterogeneous microstructures.
      \end{cvitems}
    }

  \cventry
    {Academic Project – Design of a Food Industry Lifting Trolley}
    {Centrale Lyon -- ENISE}
    {Saint-\'Etienne, France}
    {Mar. -- Jun. 2025}
    {
      \begin{cvitems}
        \item Pre-dimensioning study, strength of materials calculations, and 3D CAD modelling (SolidWorks); ran static finite element simulation (SolidWorks Simulation) to validate structural integrity.
        \item Produced full technical documentation including functional analysis, tolerancing, and manufacturing drawings.
      \end{cvitems}
    }

  \cventry
    {Academic Project – Web Application for Library Management}
    {\'Ecole des Mines de Saint-\'Etienne}
    {Saint-Étienne, France}
    {Feb. -- Jun. 2025}
    {
      \begin{cvitems}
        \item Designed and developed a full-stack library management web application using Symfony (PHP); implemented MVC architecture, database design, and user authentication.
      \end{cvitems}
    }

  \cventry
    {Academic Project – Design of a Gardening Assistance Cart}
    {Centrale Lyon -- ENISE}
    {Saint-\'Etienne, France}
    {Sep. -- Dec. 2024}
    {
      \begin{cvitems}
        \item Mechanical design and CAD modelling with SolidWorks and CATIA; functional analysis, ergonomic study, component selection, and technical documentation.
      \end{cvitems}
    }

  \cventry
    {Engineering Internship – Industrial Diagnostics \& Preventive Maintenance}
    {SOPECAM (Société de Presse et d'Éditions du Cameroun)}
    {Yaoundé, Cameroon}
    {May 2024 -- Sep. 2024}
    {
      \begin{cvitems}
        \item Investigated root causes of pump failures on KBA newspaper printing machines; proposed corrective and preventive maintenance strategies.
        \item Designed a software package for managing the preventive maintenance schedule of printing press pumps.
        \item Instrumented machines with vibration and temperature sensors; performed signal processing and failure mode analysis (FMEA approach).
      \end{cvitems}
    }

  \cventry
    {Technician Internship – Design \& Manufacturing of a 3-Axis CNC Machine}
    {FabLab -- \'Ecole Nationale Sup\'erieure Polytechnique de Yaound\'e (ENSPY)}
    {Yaoundé, Cameroon}
    {May -- Sep. 2023}
    {
      \begin{cvitems}
        \item Full CAD design (SolidWorks: assemblies, sheet metal, machining preparation) and manufacturing of a 3-axis CNC machine for prototyping and educational use.
        \item Structural sizing, component selection (linear guides, stepper motors, belt transmission), and assembly supervision.
      \end{cvitems}
    }

\end{cventries}

%-------------------------------------------------------------------------------
%  TECHNICAL SKILLS
%-------------------------------------------------------------------------------
\cvsection{Technical Skills}
\begin{cvskills}

  \cvskill
    {Mechanics \& Materials}
    {Continuum mechanics, fracture mechanics, fatigue (Dang Van, Goodman), thermo-elasticity, cohesive zone models (CZM – basics), residual stress analysis (laser spectroscopy), constitutive law identification, multi-scale modelling.}

  \cvskill
    {Materials Characterisation}
    {Vickers micro-indentation hardness testing, Scanning Electron Microscopy (SEM), Energy-Dispersive X-ray Spectroscopy (EDXS), microstructure analysis, surface integrity assessment in machining.}

  \cvskill
    {Finite Element Methods}
    {Abaqus (static, dynamic, thermal), SolidWorks Simulation, ANSYS Workbench (basics), Cast3M (basics), custom nonlinear FEM solver (Python/C++): static, modal, and transient analyses.}

  \cvskill
    {Discrete \& Stochastic Methods}
    {Discrete Element Method (DEM/LIGGGHTS), Markov chain modelling, Monte Carlo simulation, Design of Experiments (DoE), uncertainty quantification, surrogate modelling.}

  \cvskill
    {AI \& Machine Learning}
    {Physics-Informed Neural Networks (PINNs, PyTorch), inverse parameter identification, data-driven microstructure generation, deep learning for scientific computing.}

  \cvskill
    {Scientific Programming}
    {Python (NumPy, SciPy, PyTorch, Matplotlib, OpenCV, Pandas), C/C++, MATLAB (Simulink, Computer Vision, Power System toolboxes), Fortran (basics), Java, LaTeX, Git/GitHub.}

  \cvskill
    {CAD \& Design}
    {SolidWorks (assemblies, sheet metal, simulation), CATIA V5 (part design, surfacing, PLM), 3DExperience platform.}

  \cvskill
    {Signal Processing \& Instrumentation}
    {Sensors (accelerometers, thermocouples, IMU, encoders), data acquisition, vibration analysis, GR\&R, Cp/Cpk process capability analysis.}

  \cvskill
    {Web \& Software Development}
    {Python-based web applications (Gradio, Hugging Face Spaces), Symfony/PHP (MVC web apps), basic HTML/CSS.}

  \cvskill
    {Languages}
    {French (native), English (B2 – professional technical proficiency, TOEIC), German (beginner).}

\end{cvskills}

%-------------------------------------------------------------------------------
%  CERTIFICATIONS & EXTRACURRICULAR
%-------------------------------------------------------------------------------
\cvsection{Certifications \& Activities}

\begin{cventries}

  \cventry
    {Core Member – Robotics Club}
    {Centrale Lyon -- ENISE}
    {Saint-\'Etienne, France}
    {Nov. 2024 -- Present}
    {
      \begin{cvitems}
        \item Integration of sensors (IMU, encoders, temperature sensors), real-time data processing, firmware development, and collaborative project management.
      \end{cvitems}
    }

\end{cventries}

\begin{cvhonors}
  \cvhonor
    {MATLAB Certified}
    {MATLAB Onramp, Simulink Onramp, Computer Vision Onramp, Power System Onramp}
    {MathWorks}
    {2024--2025}
  \cvhonor
    {Google Advanced Data Analytics}
    {Professional Certificate – data analysis, Python, statistics, machine learning}
    {Google / Coursera}
    {2024}
  \cvhonor
    {IBM Data Analyst}
    {Professional Certificate – data analysis, visualisation, SQL, Python}
    {IBM / Coursera}
    {2024}
\end{cvhonors}

%-------------------------------------------------------------------------------
%  DEPLOYED PROJECTS
%-------------------------------------------------------------------------------
\cvsection{Open-Source \& Deployed Projects}
\begin{cvhonors}
  \cvhonor
    {FEM Fatigue Solver}
    {Nonlinear 3D FEM solver with Dang Van fatigue criterion – Python/C++ backend, interactive web interface}
    {\texttt{huggingface.co/spaces/ktongue/simulations\_apps}}
    {2026}
  \cvhonor
    {PINN Material Identification}
    {Physics-Informed Neural Network for inverse identification of constitutive law parameters from compression tests}
    {\texttt{huggingface.co/spaces/ktongue/material\_identification}}
    {2025}
\end{cvhonors}

%-------------------------------------------------------------------------------
%  ADDITIONAL INFORMATION
%-------------------------------------------------------------------------------
\cvsection{Additional Information}
\begin{cvitems}
  \item \textbf{Availability:} September/October 2026 – full geographic mobility (France and internationally).
  \item \textbf{Research interests:} Computational mechanics, granular media, fracture and fatigue, inverse problems, scientific machine learning, non-destructive evaluation (NDE), multi-physics simulation.
  \item \textbf{Soft skills:} Scientific rigour, analytical mindset, research autonomy, fast learner, team player, problem-solving orientation.
\end{cvitems}

\end{document}
